\vspace{1.0cm} \Large \bf Integrating influenza antigenic dynamics with molecular evolution

### 2013-12-06 flux.tex
Include description of example XMLs.
Fixed MAS grant numbers

Source code implementing the cartographic models has been made fully available as part of the software package BEAST \cite{BEAST17}, and can be downloaded from its Google code repository (http://code.google.com/p/beast-mcmc/).
Tutorials for implementing these models can be found at http://beast.bio.ed.ac.uk/Tutorials.
Incidence data and HI data used in this analysis is archived with Dryad (doi:10.5061/dryad.rc515).

@@

TB was supported by a Newton International Fellowship from the Royal Society. 
MAS was supported by National Institutes of Health grants R01 GM086887 and R01 HG006139 and National Science Foundation grant DMS0856099.
The research leading to these results has received funding from the European Research Council under the European Community's Seventh Framework Programme (FP7/2007-2013) under Grant Agreement no. 278433-PREDEMICS and ERC Grant agreement no. 260864.
VG, AJH and JWM were funded by MRC reference no U117512723.
AR acknowledges the support of the Wellcome Trust (grant no. 092807).
Collaboration between MAS, AR and PL was supported by the National Evolutionary Synthesis Center (NESCent), NSF EF-0423641.
DJS and CAR acknowledge EU FP7 programs EMPERIE (223498) and ANTIGONE (278976), Human Frontier Science Program (HFSP) program grant P0050/2008, Wellcome Trust 087982AIA, NIH Director's Pioneer Award DP1-OD000490-01, and National Institute of Allergy and Infectious Diseases NIH CEIRS contract HHSN266200700010C.
CAR was supported by a University Research Fellowship from the Royal Society.

>>>>

Source code implementing the cartographic models has been made fully available as part of the software package BEAST \cite{BEAST17}, and can be downloaded from its Google code repository (http://code.google.com/p/beast-mcmc/).
More details on implementing these models can be found at https://github.com/trvrb/flux/tree/master/example-xmls.
Incidence data and HI data used in this analysis is archived with Dryad (doi:10.5061/dryad.rc515).

@@

TB was supported by a Newton International Fellowship from the Royal Society. 
MAS was supported by National Institutes of Health grants R01 HG006139 and R01 AI107034 and National Science Foundation grant DMS126153 and IIS1251151.
The research leading to these results has received funding from the European Research Council under the European Community's Seventh Framework Programme (FP7/2007-2013) under Grant Agreement no. 278433-PREDEMICS and ERC Grant agreement no. 260864.
VG, AJH and JWM were funded by MRC reference no U117512723.
AR acknowledges the support of the Wellcome Trust (grant no. 092807).
Collaboration between MAS, AR and PL was supported by the National Evolutionary Synthesis Center (NESCent), NSF EF-0423641.
DJS and CAR acknowledge EU FP7 programs EMPERIE (223498) and ANTIGONE (278976), Human Frontier Science Program (HFSP) program grant P0050/2008, Wellcome Trust 087982AIA, NIH Director's Pioneer Award DP1-OD000490-01, and National Institute of Allergy and Infectious Diseases NIH CEIRS contract HHSN266200700010C.
CAR was supported by a University Research Fellowship from the Royal Society.
